---
title: 'Relationship between Sleep and Vitamin D Analysis'
subtitle: 'DATA 550 Final Report'
author: 'Alia Hiller'
date: "`r format(Sys.Date(), '%b-%d-%y')`"
output: html_document

---
```{r, setup, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, load-data}
here::i_am('FinalReport_Hiller.Rmd')

data <- readRDS(
  file = here::here('output/clean_data.rds')
)
```

# __Introduction__

This data is from the CDC's 2017-2018 National Health and Nutrition Examination Surveys (NHANES), a nationally representative, cross-sectional survey of adults and children in the United States. This analysis aims to:

* Describe the characteristics of the study sample
* Examine the relationship between hours of sleep and vitamin D levels

# __Descriptive Analysis__

## Table 1

Table 1 provides descriptive statistics for this dataset.

```{r, table1}
table1 <- readRDS(
  file = here::here('output/table1.rds')
)

table1
```


## Figure 1

Figure 1 shows the relationship between hours of sleep and vitamin D levels (nmol/L).

```{r, plot-data}
#| fig.align = "center",
#| out.width = "600px"

knitr::include_graphics(
  here::here('output/figure1.png')
)
```
